Update Meeting: 14-07-2021

### 2021-07-22 analysis/update_meeting_05_07_2021.Rmd
Updating website

```{r sex_het, echo = FALSE}

tar_load(household_MR_exhaustive_summary)

household_MR_exhaustive_summary <- household_MR_exhaustive_summary %>% mutate(same_traits = case_when(exposure_ID == outcome_ID ~ TRUE, 
                                                                   TRUE ~ FALSE))

@@

## Questions.

>>>>

```{r univar_mr, echo = FALSE}

household_MR_exhaustive_summary <- readRDS("household_MR_exhaustive_summary.rds")
traits_corr2_update <- readRDS("traits_corr2_update.rds")
traits_corr2_update <- traits_corr2_update[which(traits_corr2_update[["Neale_file_sex"]]=="both"),]

description_temp <- left_join(household_MR_exhaustive_summary, traits_corr2_update[, c("Neale_pheno_ID", "description")], by=c("exposure_ID"="Neale_pheno_ID")) %>%
  rename(exposure_description = description)

description <- left_join(description_temp, traits_corr2_update[, c("Neale_pheno_ID", "description")], by=c("outcome_ID"="Neale_pheno_ID")) %>%
  rename(outcome_description = description)

household_MR_exhaustive_summary <- description %>% mutate(same_traits = case_when(exposure_ID == outcome_ID ~ TRUE, 
                                                                   TRUE ~ FALSE)) %>% dplyr::select(-exposure, -outcome) %>%
  dplyr::select(-Egger_summary, -Egger_pval, -Egger_int_pval, -Het_IVW_Qpval, -N_snps_sensitivity, -`IVW/Wald_summary_sensitivity`, -`IVW/Wald_pval_sensitivity`, -outcome_sex)

@@

- Number of BF-significant results: 
```{r BF_sig, echo = FALSE}

BF_sig <- household_MR_exhaustive_summary %>% rename(IVW_Wald_pval= `IVW/Wald_pval`) %>% 
  mutate_at("IVW_Wald_pval", as.numeric) %>% filter(IVW_Wald_pval < 0.05/dim(.)[1])

dim(BF_sig)

- Significant results not in the same trait

```{r non_same_traits, echo = FALSE}

diff_traits <- BF_sig %>% filter(same_traits==FALSE)
DT::datatable(diff_traits, width = "100%")

```
## Questions.

### 2021-07-22 analysis/update_meeting_14_06_2021.Rmd
Updating website

>>>>

### Getting back up to speed.

- Project had been dormant for > 1 year. 
- Since then, one key paper has been published in Nature Communications by Tenesa et al: [Evidence of horizontal indirect genetic effects in humans](https://www.nature.com/articles/s41562-020-00991-9).
- Discussed where we left off and how to build on Tenesa paper.
- Slides can be found [here](presentations/Xia_horizontal_genetic_effects/presentation.html#1).

### 2021-07-22 analysis/update_meeting_14_07_2021.Rmd
update meeting
Updating website

options(scipen=999)
source("code/settings.R")
load("summary.Rdata")
library(DT)
library(knitr)
library(targets)

@@

```{r new_phenos, echo = FALSE}

@@

```{r pc_corr, echo = FALSE}

@@

$$
\begin{eqnarray*}
	(1) \; X_{i} &=& G_{i}\cdot {\beta_{x, i\rightarrow i} } + \epsilon \\
	(2) \; X_{p} &=& G_{i}\cdot {\beta_{x, i\rightarrow p} } + \epsilon \\
	(3) \; Y_{i} &=& G_{i}\cdot {\beta_{y, i\rightarrow i} } + \epsilon \\
	(4) \; Y_{p} &=& G_{i}\cdot {\beta_{y, i\rightarrow p} } + \epsilon \\
	(5) \; Y_{i} &=& \alpha_j\cdot X_{i} +\epsilon \\
	(6) \; X_{p} &=& \alpha_{x, am}\cdot X_{i{}} +\epsilon \\
	(7) \; Y_{p} &=& \alpha_{y, am}\cdot Y_{i{}} +\epsilon \\
	(8) \; Y_{p} &=& \alpha_{k}\cdot X_{i} +\epsilon

\end{eqnarray*}
$$

@@

>>>>

options(scipen=999)
source("code/settings.R")

library(DT)
library(knitr)
library(targets)
```

@@

```{r new_phenos, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}

@@

```{r pc_corr, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}

@@

BREAK1

$$
    \(1) \; X_{i} = G_{i}\cdot {\beta_{x, i\rightarrow i} } + \epsilon \\
    \(2) \; X_{p} = G_{i}\cdot {\beta_{x, i\rightarrow p} } + \epsilon \\
    (3) \; Y_{i} = G_{i}\cdot {\beta_{y, i\rightarrow i} } + \epsilon \\
	  (4) \; Y_{p} = G_{i}\cdot {\beta_{y, i\rightarrow p} } + \epsilon \\
	  (5) \; Y_{i} = \alpha_j\cdot X_{i} +\epsilon \\
	  (6) \; X_{p} = \alpha_{x, am}\cdot X_{i{}} +\epsilon \\
	  (7) \; Y_{p} = \alpha_{y, am}\cdot Y_{i{}} +\epsilon \\
	  (8) \; Y_{p} = \alpha_{k}\cdot X_{i} +\epsilon

$$

BREAK2

\begin{equation}
	 \; X_{p} = G_{i}\cdot {\beta_{x, i\rightarrow p} } + \epsilon \\
	 \; Y_{i} = G_{i}\cdot {\beta_{y, i\rightarrow i} } + \epsilon \\
	 \; Y_{p} = G_{i}\cdot {\beta_{y, i\rightarrow p} } + \epsilon \\
	 \; Y_{i} = \alpha_j\cdot X_{i} +\epsilon \\
	 \; X_{p} = \alpha_{x, am}\cdot X_{i{}} +\epsilon \\
	 \; Y_{p} = \alpha_{y, am}\cdot Y_{i{}} +\epsilon \\
	 \; Y_{p} = \alpha_{k}\cdot X_{i} +\epsilon
\end{equation}

BREAK3

$$
	 \; X_{p} = G_{i}\cdot {\beta_{x, i\rightarrow p} } + \epsilon \\
	 \; Y_{i} = G_{i}\cdot {\beta_{y, i\rightarrow i} } + \epsilon \\
	 \; Y_{p} = G_{i}\cdot {\beta_{y, i\rightarrow p} } + \epsilon \\
	 \; Y_{i} = \alpha_j\cdot X_{i} +\epsilon \\
	 \; X_{p} = \alpha_{x, am}\cdot X_{i{}} +\epsilon \\
	 \; Y_{p} = \alpha_{y, am}\cdot Y_{i{}} +\epsilon \\
	 \; Y_{p} = \alpha_{k}\cdot X_{i} +\epsilon
$$

@@

$$
\sqrt{p}
$$

$$
x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
$$
